Supplement to Global Distribution of Unintended Pregnancies and Contraceptive Usage Project

### 2024-04-29 code/analysis-code/statistical-analysis.qmd
Part 6 Updates
Removed the slides folder. Responded to Kevin's feedback to fix supplement error and update READMe files throughout.

# create a professional format of the table to add to the manuscript 
kable_lmtable11 <- kable(lmtable11)

# save fit results table  
table_file16 = here("results", "tables", "resulttable16.rds")
saveRDS(kable_lmtable11, file = table_file16)
```
As expected, the coefficients are much smaller than the first full model we created without the regularization penalty, but all 5 predictors remain in the model. The `sarc_standard` predictor still has the strongest relationship with the outcome. The percent of women currently married, rate of maternal deaths due to unintended pregnancies, and rate of maternal deaths to due to abortion all have weak negative associations with the outcome. The direction of the relationship between the rate of maternal deaths due to abortions and the outcome flipped from the first full regression model to this model, but the coefficient is so small that this difference is not significant.

>>>>

# create a professional format of the table to add to the manuscript 
lmtable11 <- as_flextable(lmtable11)

# save fit results table  
table_file16 = here("results", "tables", "resulttable16.rds")
saveRDS(lmtable11, file = table_file16)
```
As expected, the coefficients are much smaller than the first full model we created without the regularization penalty, but all 5 predictors remain in the model. The `sarc_standard` predictor still has the strongest relationship with the outcome. The percent of women currently married, rate of maternal deaths due to unintended pregnancies, and rate of maternal deaths to due to abortion all have weak negative associations with the outcome. The direction of the relationship between the rate of maternal deaths due to abortions and the outcome flipped from the first full regression model to this model, but the coefficient is so small that this difference is not significant.

### 2024-04-29 products/manuscript/Manuscript.qmd
Part 6 Updates
Removed the slides folder. Responded to Kevin's feedback to fix supplement error and update READMe files throughout.

The predictor variables will include the total number of people women using each type of birth control standardized by population size, region, percentage of women currently married, percentage of women never married, total rate of maternal deaths, rate of maternal deaths due to unintended pregnancy and rate of maternal deaths due to abortion.

@@

>>>>

The predictor variables will include the total number of women using each type of birth control standardized by population size, region, percentage of women currently married, percentage of women never married, total rate of maternal deaths, rate of maternal deaths due to unintended pregnancy and rate of maternal deaths due to abortion.

@@

We hypothesize that the percentage of unintended preggnancies among SARC users will vary between the five regions based on differing access to this type of contraception.

### 2024-04-29 products/manuscript/supplement/Supplementary-Material.qmd
Part 6 Updates
Removed the slides folder. Responded to Kevin's feedback to fix supplement error and update READMe files throughout.

# Additional data cleaning explanation
The first priority when cleaning the data was analyzing missing values, and our findings can be seen @tbl-summarytable. We found that the `pct_upreg` variable containing the percentage of unintended pregnancies is unreliable due to missing data that could not be explained. This variable is only 82% complete, but the individual percent of unintended pregnancy variables correponding with different types of birth control methods are each 100% complete. Since the missingness of this data is not well explained except by the hypothesis that this variable was found using methods outside of the AIU protocol, we decided to use the variables with percentage of unintended pregnancies related to each birth control method as our outcome variables because they are complete and were found directly based on the AIU protocol information. We printed the summary table here because it was useful in determining missingness and creating a new factor variable for the usage of each birth control method at the factor level later in the processing sequence. 
```{r}
#| label: tbl-summarytable2
#| tbl-cap: "Summary table to discover missingness"
#| echo: FALSE
resulttable2 <- readRDS("../../results/tables/summarytable.rds")
kable(resulttable2)
```

>>>>

# Additional data cleaning explanation
The first priority when cleaning the data was analyzing missing values, and our findings can be seen @tbl-summarytable2. We found that the `pct_upreg` variable containing the percentage of unintended pregnancies is unreliable due to missing data that could not be explained. This variable is only 82% complete, but the individual percent of unintended pregnancy variables correponding with different types of birth control methods are each 100% complete. Since the missingness of this data is not well explained except by the hypothesis that this variable was found using methods outside of the AIU protocol, we decided to use the variables with percentage of unintended pregnancies related to each birth control method as our outcome variables because they are complete and were found directly based on the AIU protocol information. We printed the summary table here because it was useful in determining missingness and creating a new factor variable for the usage of each birth control method at the factor level later in the processing sequence. 
```{r}
#| label: tbl-summarytable2
#| tbl-cap: "Summary table to discover missingness"
#| echo: FALSE
resulttable2 <- readRDS(here("results", "tables", "summarytable.rds"))
kable(resulttable2)
```
